---
title: "Hyundai-OilDetection"
output: html_document
date: "2022-11-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Science Competition Hyundai Genuine Oil Detection

### Summary

Evaluate oil condition in heavy equipment by developing a binary classification machine learning model (i.e. normal, faulty)


### Code

We download and load the necessary packages below

```{r}

my_packages <- c("dplyr", "caret", "ROSE", "smotefamily", "ggplot2")

lapply(my_packages, require, character.only = TRUE)

```

*Data Import*

We import the datasets below
```{r}

train <- read.csv(file.path(getwd(),"Data","train.csv"))
test <- read.csv(file.path(getwd(),"Data","test.csv"))
sampleSubmission <- read.csv(file.path(getwd(),"Data","sample_submission.csv"))

```


Only select columns of the training data is available in the test data (and in actual work environment) therefore we only use relevant columns.

```{r}

#select only columns available in test for train
train <- train %>% select(colnames(test),Y_LABEL)

```

### Exploratory Data Analysis

```{r}
#observe summary statistics
summary(train)
```

Observing the summary statistics many variables are skewed to the left - the min and median values are mostly 0, whereas max values are high. We visualize this below.

```{r}

#store numeric independent variables


#create dataframe with only numeric columns
num_cols <- unlist(lapply(train, is.numeric))
num_data <- train[,num_cols]

#get column names and drop dependent variable
num_cols <- colnames(num_data)
num_cols <- num_cols[num_cols != "Y_LABEL"]

for(var in num_cols){
  plot(train[,var], train$Y_LABEL, xlab = var)
}
```

### Class Imbalance


We observe distribution of the binary dependent variable below.
```{r}

table(train$Y_LABEL)

```

We observe class imbalance. We utilize sampling methods to fix this below.

1. Upsampling
2. ROSE Sampling
3. SMOTE Sampling

```{r}

# Upsampling


# ROSE Sampling


# SMOTE Sampling


```


### Model Building

We explore different models below: neural network, gradient boosting, etc.

```{r}



```



